---
title: "lab11"
author: "Haoqiu Wu"
date: "2018Äê3ÔÂ26ÈÕ"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##association rules

we saw assciations rule in the context of actual transcations, but they can also be viewed on the categorical data by using what is commonly called one-hot encoding

all it means is making an indicator variable for each level of the factor. the arules package can coerce factors into the desiered form.

let us check out some survey data...

two packaged needed "arules" and "effects"

```{r}
library(effects)
library(arules)

data(WVS)
head(WVS)
summary(WVS)
#convert a numerical variable to a categorical variable
WVS$age=discretize(WVS$age,method="interval", breaks=4)#want four groups
table(WVS$age)

asurv=apriori(WVS)
summary(asurv)

inspect(sort(asurv,by="support")[1:10])
inspect(sort(asurv,by="confidence")[1:10])
inspect(sort(asurv,by="lift")[1:10])
inspect(sort(asurv,by="support",decreasing = FALSE)[1:10])

asurv=apriori(WVS,parameter = list(supp=0.04,conf=0.8))
summary(asurv)
#now look at the association rule after the changing the thresholds

inspect(sort(asurv,by="support")[1:10])
inspect(sort(asurv,by="confidence")[1:10])
inspect(sort(asurv,by="lift")[1:10])
inspect(sort(asurv,by="support",decreasing = FALSE)[1:10])

