---
title: "lab3"
author: "Haoqiu Wu"
date: "2018Äê1ÔÂ22ÈÕ"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## write functioons in r -basis
let us learn the structure of writing our own functions.to learn syntax, we will simly
make a function that adds 10 to any inputed value

```{r}
shift10=function(x){
    newx=x+10
    newx
}
```
note that the final line in the functionn will be the outputted value

```{r}
y=shift10(40)
y
```

in many of the artistic sports, the judging panel is comprised of serveral countries and a participant score is averaged after removing minimum and maximum values

write a function which performs this type of averaging for any inputted vector of numeric values.
call it olymean

```{r}
olymean=function(x){
    sort_x=sort(x)
    trim_x=sort_x[-c(1,length(x))]
    mean(trim_x)
}
```

test this function based on faithful dataset
```{r}
mean(faithful$waiting)
olymean(faithful$waiting)
```

what if your input dataset has missing value

```{r}
mean(airquality$Ozone)
olymean(airquality$Ozone)
#becaue sort funtion has omitted the na value
``` 
the mean function has issues with nas, we can fix that  by setting option na.rm=TRUE
```{r}
mean(airquality$Ozone,na.rm = TRUE)
```

## analyses from lecture
here are the simple and multiple linear regression models as fit on the life expectancy data
```{r}
stdata=data.frame(state.x77)
slr=lm(stdata$Life.Exp~stdata$Illiteracy)
summary(slr)

mlr=lm(stdata$Life.Exp~stdata$Illiteracy+stdata$Murder+stdata$HS.Grad+stdata$Frost)
summary(mlr)
```

here are the model fittings provided for the body data set
```{r}
library("gclus")
data(body)
simlm=lm(body$Weight~body$Height)
mutlm=lm(body$Weight~body$Height+body$Gender)
summary(mutlm)
summary(simlm)
``` 
note that the gender variable is recorde as 0 and 1. many times, the data will be in a character string form
```{r}
head(body$Gender)
body$Gender[body$Gender==1]="Male"
body$Gender[body$Gender==1]="Female"
```
what happens if we fit the model now?
``` {r}
multlm=lm(body$Weight~body$Height+body$Gender)
summary(multlm)
```
some functions may have no problem figuring out to do with character strings, other times we may have to tell r to treat them as categories
this is generally done with the 'factor' command
```{r}
body$Gender=factor(body$Gender)
multlm=lm(body$Weight~body$Height+body$Gender)
summary(multlm)
```

we may be interested in changing the reference level for the creation of dummy variables
the relevel command can take care of this
```{r}
body$Gender=relevel(factor(body$Gender),ref = "Male")
multlm=lm(body$Weight~body$Height+body$Gender)
summary(multlm)
```
finally we can fit the model with interactions
```{r}
intlm=lm(body$Weight~body$Height*body$Gender)
summary(intlm)
```

now look at quadratic simulation

```{r}
set.seed(3531)
x=runif(30,-2,2)
y=15+2.3*x-1.5*x^2+rnorm(30)

plot(y~x)
linmod=lm(y~x)
abline(linmod,col="blue",lwd=3)

x2=x^2
quadmod=lm(y~x+x2)
summary(quadmod)
```

```{r}
plot(y~x)
curve(15.35+2.27*x-1.67*x^2,add=TRUE,col="red",lwd=3)
```
KNN. we will have to install the FNN packages
```{r}
library(FNN)
xmat=cbind(x,x2)
seqx=seq(from=-2,to=2,by=0.001)

plot(y~x,main="k=20 Green,k=5 Purple,k=1 Brown")

knnr20=knn.reg(xmat,y=y,test=cbind(seqx,seqx^2),k=20)
lines(seqx,knnr20$pred,col="green",lwd=1)

knnr5=knn.reg(xmat,y=y,test=cbind(seqx,seqx^2),k=5)
lines(seqx,knnr5$pred,col="purple",lwd=1)

knnr1=knn.reg(xmat,y=y,test=cbind(seqx,seqx^2),k=1)
lines(seqx,knnr1$pred,col="brown",lwd=1)

plot(y~x)
abline(linmod,col="blue",lwd=3)#linear model

curve(15.35+2.27*x-1.67*x^2,add=TRUE,col="red",lwd=3)#quadratic model

lines(seqx,knnr5$pred,col="purple",lwd=3)#knn reg,k=5

curve(15+2.3*x-1.5*x^2,add = TRUE,col="black",lty="dashed")#true model(since simulated)