---
title: "lab10"
author: "Haoqiu Wu"
date: "2018Äê3ÔÂ19ÈÕ"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### PCA on cars

let us run pca on the car93.csv data set that we looked at on the last assignment

```{r}
card=read.csv("E:/car93.csv",stringsAsFactors = FALSE)

pcard=prcomp(as.matrix(card[,-c(1,2,3)]),scale. = TRUE)

summary(pcard)
```

according to the kaiser criterion,we would retain 2 components which explain 78% of the variation in the data.

```{r}
biplot(pcard)

```

note that this is equivalent to plotting the scores(projected/rotated data)

```{r}
plot(pcard$x[,1:2])

plot(pcard$x[,1:2],type="n")
text(pcard$x[,1],pcard$x[,2],labels = 1:nrow(card))
```

let us take a look at the component loadings(eigenvectors), which prvide the coefficients for the original variables

```{r}
round(pcard$rotation[,1:2],2)

```

for he first component, magnitudes of the coefficients are pretty similar across the board,

but some are positive and some are negative

positive ones:most of these measurements have something to do with size of the vehicle

negative ones: related to fuel efficiency(which would be generally nagatively correlated with size)

we can broadly interpret this first components as "size"  of the car

the second component is a little less clear, focus on the larger magnitudes

```{r}
round(pcard$rotation[,2],2)[abs(pcard$rotation[,2])>.2]
```

so we have high positive loadings for price, horsepower and rpm, along with large nagative loadings for mpg, rear seats and luggage.

we would expect that this is maybe describing sports cars.

we could consider this a measure of sportiness... relatively small , expensive cars with a strong engines

this makes sense from a rotation standpoint. if the bulk of the variation (first component) will measure cars based on theri size contrasted with fuel efficiency, then sports cars would not fit in with the rest of the data on this component

sports cars are small and not fuel efficient.

proof of concept on these components :
here are the four cars that score the highest on PC1(size):

```{r}
card[order(pcard$x[,1],decreasing=TRUE)[1:4],1:3]
```

four that score highest on PC2(sportness):
```{r}
card[order(pcard$x[,2],decreasing=TRUE)[1:4],1:3]

```

only the first is actually designated "sporty", though the next 3 are luxury, midsize vehicles. Maybe interpret this component as "luxuriousness", but either way, cars that score highly on PC2 are going to be expensive and fuel inefficient relative to their size.

##clustering on PCA
```{r}
test1=hclust(dist(scale(card[,-c(1:3)])))
plot(test1)

test2=hclust(dist(pcard$x))
plot(test2)

all.equal(dist(scale(card[,-c(1:3)])),dist(pcard$x),check.attributes=FALSE)

all.equal(dist(scale(card[,-c(1:3)])),dist(pcard$x[,1:2]),check.attributes=FALSE)

```


clustering on the first two components

```{r}
pcclust=hclust(dist(pcard$x[,1:2]))
plot(pcclust)
```

dendrogram suggests two groups

```{r}
table(card$Type,cutree(pcclust,2))

```

this table shows that the predominant group structure on the first two PCs separates out the smaller cars(Compact, Small, Sporty) and larger cars(Midsize,large)

###FA on Cars

fit for two factors

```{r}
facar=factanal(card[,-c(1,2,3)],2,scores = "regression")
facar
```

the print method will leave empty any coefficients that fall below a threshold(~<0.1).

we can appproximately see the same amount of variation described by two factors(74.5) as was by PCA (78%)

they are fairly similar in terms of loadings

p-value is highly significant, the null hypothesis that 2 factors are sufficient for fitting the data... sor the p-value is telling us that there is evidence to suggest that 2 factors are not sufficient.

```{r}
plot(facar$scores)

faclust=hclust(dist(facar$scores))
plot(faclust)

table(card[,3],cutree(faclust,3))
```


why are some of the midsize cars in group 2 and some in group3?

```{r}
cgroups=cutree(faclust,3)

card[cgroups==2 & card$Type=="Midsize",1:3]

card[cgroups==3 & card$Type=="Midsize",1:3]

```

so we get groups that are approoximatelu:"smaller cars","luxury midsize cars" and "larger cars"

##PCA lecture example posted on connect

